\documentclass[12pt,oneside,english]{matchapter}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=1.5cm,lmargin=1.4cm,rmargin=1.4cm}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{pdfcomment}
\usepackage{cooltooltips}
\usepackage{framed}
\usepackage{graphics,hyperref}
\usepackage{imakeidx}


\makeatletter
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\newtheorem*{definition}{\color{blue} Definition}
\newtheorem*{vocab}{\color{purple} Vocabulary}
\newtheorem*{fact}{\color{green} Fact}
\newtheorem*{warn}{\color{red} Warning}
\newtheorem{task}{Task}
\newtheorem{exercise}{Exercise}
\newtheorem{question}{Question}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}


\DeclareMathOperator{\w}{\hyperref[sec:Writ]{Writing}}
\DeclareMathOperator{\W}{\hyperref[sec:Writ]{\textbf{Writing}}}
\DeclareMathOperator{\con}{\hyperref[sec:Concep]{Conceptual}}
\DeclareMathOperator{\CON}{\hyperref[sec:Concep]{\textbf{Conceptual}}}
\DeclareMathOperator{\com}{\hyperref[sec:Compu]{Computational}}
\DeclareMathOperator{\COM}{\hyperref[sec:Compu]{\textbf{Computational}}}
\DeclareMathOperator{\vg}{\hyperref[sec:Visgeo]{Visual/Geometry}}
\DeclareMathOperator{\VG}{\hyperref[sec:Visgeo]{\textbf{Visual/Geometry}}}

\DeclareMathOperator{\R}{\mathbb{R}}

% Allow an index to be created
\makeindex[title=Index of Terms, columns=3]
\makeindex[name=definitions, title=Index of Definitions, columns=3]
\makeindex[name=symbols, title=Index of Symbols, columns=3]

\indexsetup{
	level=\Heading,
	noclearpage
}

\makeatother
\newtheorem{problem}{Problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newif\ifshowCom
\newif\ifshowCon
\newif\ifshowW
\newif\ifshowVG

\showComtrue
%\showComfalse
\showContrue
%\showConfalse
\showWtrue
%\showWfalse
\showVGtrue
%\showVGfalse

\input{Learning_Standards_Revised-Summer-2023/concepts}

\begin{document}



\section*{All Goals}
	

\section*{By Chapter}

\subsection*{Chapter 0}
\begin{enumerate}
    \ifshowW
	\item I can describe sets using the set builder notation ($\w$). 
	\fi
    \ifshowCom
	\item I can perform algebraic arithmetic on vectors in $\R^n$ (e.g., addition, scalar multiplication, norm, dot product, and cross product) ($\com$).
	\fi
    \ifshowVG
	\item I can represent vector arithmetic geometrically for vectors in $\R^2$ and $\R^3$ ($\vg$).
	\fi
    \ifshowCon
	\item I can decide whether given vectors are parallel ($\con$).
	\fi
    \ifshowCon
    \item I can decide whether given vectors are perpendicular ($\con$).
	\fi
    \ifshowCom
    \item I can compute the angle between any two vectors ($\COM$).
	\fi
    \ifshowCon
	\item I can represent a line in $\R^2$ and $\R^3$ in vector form ($\con$).
	\fi
    \ifshowCon
    \item I can represent a line in $\R^2$ and $\R^3$ in parametric form ($\con$).
	\fi
    \ifshowVG
	\item Given an algebraic description of a line in $\R^2$ or $\R^3$, I can visualize the line ($\vg$).
	\fi
    \ifshowCon
	\item I can represent a plane in $\R^3$ given a normal vector and a point ($\CON$).
	\fi
    \ifshowVG
	\item Given the normal form of a plane in $\R^3$, I can visualize the plane ($\VG$).
	\fi
\end{enumerate}

\subsection*{Chapter 1}
\begin{enumerate}
	\item I can express a linear system in terms of an augmented matrix and as a matrix-vector equation. 
	\item I can perform row reduction (by hand and in MATLAB) on any matrix and reduce it to REF or RREF.
	\item Given an RREF of an augmented matrix of a system of linear equations, I can identify free and basic variables, and describe the general solution to the system in set builder notation.
	\item Given REF of an augmented matrix of a system of linear equations, I can decide what type of solution the system has: no solution, a unique solution and infinitely many solutions.
	\item Given the general solution to a system of linear equations, I can find the particular solution(s).
	\item \textbf{Given a system of linear equations with two or three variables I can visualize\footnote{throughout standards, "I can visualize" means that I can picture it in my head, and I can draw it on a paper and I can verify my drawing using technology} the system and its general solution  }
	\item I can connect statements about rank of $A$ to statements about solution types of $[A |\vec b]$. (see Ex 2 and 3 and 4 in sec 1.3)
	\item I can represent a system of linear equations in its matrix form and vice versa.
	\item I can rephrase solving a linear system into a statement about writing a vector as a linear combination of other vectors and vice versa. 
	\item \textbf{Given the matrix form $A\vec x=\vec b$ of a linear system, as long as $A$ has less than 3 columns, I can visualize the linear system in terms of writing $\vec b$ as a linear combination of columns of $A$. }
	\item I can add matrices of the same size, multiply a matrix by a scalar and I can multiply a matrix into a vector if the sizes match up. 
	\item I can interpret matrix-vector multiplication in terms of a linear combination of the columns of the matrix.
    \item I can visualize a linear combination of two vectors in $\mathbb R^2$ and $\mathbb R^3$.
\end{enumerate}

\subsection*{Chapter 2}
\begin{enumerate}
	\item Given a linear transformation in any form I can determine its domain and codomain. 
	\item Given a function from $\R^n$ to $\R^m$ I can apply the definition of the linear transformation or the Linear Transformation or the Matrices theorem to decide whether it is a linear map. 
	\item Given a linear transformation $T$ in any form I can find $T(\vec x)$ for any vector $\vec x$. 
	\item Given the output of a linear transformation $T$ of enough\footnote{what does enough mean here?} number of vectors, I can use linearity to compute the standard matrix representation of $T$. 
	\item \textbf{Given a linear transformation with domain and codomain in $\R^2$ or $\R^3$ I can visualize the effect of the transformation on the unit square or the unit cube.}
	
	\item I recognize the standard representations of the geometric transformations in $\R^2$. \footnote{Here, by geometric linear transformations we mean scaling, orthogonal projection, reflection, rotation, rotation combined with scaling, shear.}
	\item I can find (not memorize) the standard matrix representation of the geometric representations on $\R^2$. 
	\item \textbf{I can visualize the effect of the geometric linear transformations on $\R^2$ and $\R^3$.}
	 
	\item Given two linear transformations $T$ and $S$, in any form, I can decide whether or not $S\circ T$ and $T\circ S$ are defined. 
	
	\item \textbf{I can visualize the effect of the composition of two linear transformations on a given vector in $\R^2$ and $\R^3$. }
	
	\item Given the standard matrix of linear transformations $T$ and $S$, I can compute the standard matrix of $T\circ S$ or $S\circ T$ (if defined).
	\item Given matrices $A$ and $B$, I can compute $AB$, if defined, in two different ways: 1) applying $A$ to the columns of $B$ using the matrix-vector multiplication, 2) finding the $ij$-th entry of $AB$ directly by computing the dot product between the $i$th row of $A$ and the $j$th column of $B$. 
	%(see Theorem 2.3.4 and Theorem 2.3.2).
	\item Given matrices $A$ and $B$, I can interpret $AB$, if defined, as the standard matrix representation of the composition of two linear transformations. 
	\item I know the algebraic properties of matrix multiplication. 
	%(see Theorem 2.3.5-Theorem 2.3.8)
	\item Given a linear transformation $T$ and its standard matrix $A$, I can perform row reduction on $A$ to decide whether $T$ is invertible. If $T$ is invertible, I can find its inverse map $T^{-1}$, and the standard matrix representation of $T^{-1}$, denoted by $A^{-1}$. 
	\item I can use the inverse of a matrix, if exists, to solve a linear system.
	\item I know algebraic properties of inverses 
	%(see Theorem 2.4.7 and Theorem 2.4.8)
	\item I can find the inverse of an invertible $2\times 2 $ matrix without row reduction. 
	%(see Theorem 2.4.9)
	\item I can rephrase the statement "The linear transformation $T$ is invertible" in terms of the standard matrix representation of $T$.
	\item I can rephrase the statement "The linear transformation $T$ is invertible" in terms of the type of solution of a system of linear equation. 
	
	\item Given a linear transformation $T(\vec x)=A\vec x$, I can rephrase "$T$ is injective" in terms of the solution type to $A\vec x=\vec 0$, and in terms of the REF and RREF of $A$. \label{inj}
	
	
	\item Given a linear transformation $T(\vec x)=A\vec x$, I can rephrase "$T$ is surjective" in terms of the solution type to $A\vec x=\vec b$ for an arbitrary $\vec b$ in the codomain of $T$ and in terms of REF and RREF of $A$. \label{surj}
	
	
	\item I can rephrase the statement "The linear transformation $T$ is invertible" using the words injective and surjective. \label{invertiobleIII}

	
\end{enumerate}

\subsection*{Chapter 3}

\subsection*{Chapter 4}

\subsection*{Chapter 5}

\subsection*{Chapter 6}

\subsection*{Chapter 7}

\subsection*{Chapter 8}


\section*{By Category}

\subsection*{Computational}
\label{sec:Compu}

\subsection*{Conceptual}
\label{sec:Concep}

\subsection*{Visual/Geometry}
\label{sec:Visgeo}

\subsection*{Writing}
\label{sec:Writ}

\end{document}